---
title: "adsir_hw_4"
author: "Jake Greenberg"
date: "4/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Regular expressions
library(tidyverse)        # contains stringr for regex
library(googlesheets4)    # for reading in data
gs4_deauth()              # to read in google sheet (or download)

#tmap
library(tmap)
library(pacman)
library(gifski)          # not needed since you won't do animated graphs

theme_set(theme_minimal()) # Lisa's favorite theme
```

https://github.com/jgreenb4/adsir_hw_4

# Regular Expressions

```{r}
bestsellers <- read_sheet("https://docs.google.com/spreadsheets/d/1n3xKHK4-t5S73LgxOJVJWT5fMYjLj7kqmYl1LHkpk80/edit?usp=sharing")
```

1. Find books with multiple authors (HINT: Consider the possibility of an author having “and” in their name)

```{r}
 bestsellers %>% 
  mutate(duplicate_authors = str_detect(author, "\\sand\\s")) %>% 
  filter(duplicate_authors == "TRUE") %>% 
  select(title, author, duplicate_authors)
```

2. Detect if the author’s first name starts with a vowel


```{r}
bestsellers %>% 
  mutate(vowel = str_detect(author, "^[AEIOU]")) %>% 
  filter(vowel == TRUE) %>% 
  select(author, title, vowel)
```


3. Change all authors with the name Alexander to Alex

```{r}
bestsellers %>% 
  mutate(checking = str_detect(author, "^Alexander"), names = str_replace_all(author, "Alexander", "Alex")) %>% 
  filter(checking == T) %>% 
  select(author, names)
```


4. Find books that are the second book in a series

```{r}
bestsellers %>%
  mutate(series = str_detect(description, 
                          pattern = "sequel")) %>%
  filter(series == TRUE) %>% 
  select(title, description)
```

5. Find books that are the third or fourth one in a series

```{r}
bestsellers %>%
  mutate(series = str_detect(description, 
                          pattern = "(third|fourth) book")) %>%
  filter(series == TRUE)
```


6. Find books that are the 10th, 11th, …, or 19th book in a series

```{r}
bestsellers %>%
  mutate(series = str_detect(description,
                          pattern = "1[0-9]th book")) %>%
  filter(series == TRUE)
```

7. Describe in your own words how you would go about writing a regular expression for password pattern matching (ie 8 character minimum, one capital letter minimum, one lowercase letter minimum, one digit minimum, one special character minimum).

In writing a regular expression for password pattern matching, I would write different clauses to ensure that each of the criteria for a valid password is met. I would start by ensuring that the password is at least 8 characters long with the clause, nchar(password) >= 8, where the password is stored by the variable, password. Next, I would use str_detect to ensure that there is at least one capital letter, lowercase letter, number, and special character, as shown in the above examples.


# Tmap Exercises 

```{r}
data("World")
```

```{r}
data("metro")
```

1. Make a world map using the base World dataset we used with the COVID example. Add information about income groups (income_grp) to the plot, specify a color palette.

```{r}
# let's explore the variable names of each dataset
names(World)
names(metro)
```

```{r}
# Set your mode
tmap_mode('plot')

tm_shape(World) +
    tm_polygons("income_grp", 
                palette="-Greens", 
                contrast= .9, # this sees to lead to the clearest distinctions
                id="name", 
                title="Income group")
```

2. To the plot from (1), add the new dataset metro to the plot, and add information about cities’ populations in 2020.

```{r}
# Set your mode
tmap_mode('plot')

tm_shape(World) +
  tm_polygons("income_grp", 
              palette="-Greens", 
              contrast= .9, 
              id="name", 
              title="Income group") +
  tm_shape(metro) +
  tm_bubbles("pop2020", 
        contrast=1, 
        title.size="Metro population", 
        id="name")  #HINT: what other tm_type can we add here?
```

3. Now, make a new plot with the World data that provides a look at country economic status and the inequality associated with each.



```{r}
# Set your mode
tmap_mode('plot')

tm_shape(World) +
  tm_polygons("economy") +
  tm_bubbles("inequality", 
             border.alpha = .5) +
  tm_format("World_wide")
```

4. Using a new data set, NDL_muni municipality data from the Netherlands, create a plot with two separate maps. One showing the percentage of men per municipality of the whole country, and one showing the same but faceted by province.

```{r}
tmap_mode("plot")

data(NLD_muni)

NLD_muni <- NLD_muni %>% 
  mutate(perc_men = pop_men / population * 100)

NLD_mpm <- tm_shape(NLD_muni) + 
  tm_polygons("perc_men", 
              palette = 'RdYlBu')

NLD_mpm_fct <- tm_shape(NLD_muni) +
    tm_polygons("perc_men", 
                palette = "RdYlBu") +
    tm_facets(by = "province")

tmap_arrange(NLD_mpm, NLD_mpm_fct)
```

